% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}

\documentclass[]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi

% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
  \usepackage{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
  \usepackage[left=2.5in,bottom=1.25in,top=1.25in,right=1in]{geometry}
  \ifxetex
\usepackage[setpagesize=false, % page size defined by xetex
            unicode=false, % unicode breaks when used with xetex
            xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
bookmarks=true,
pdfauthor={},
pdftitle={Preregistration BIOL 520I - Productivity and Reproducibility},
colorlinks=true,
citecolor=blue,
urlcolor=blue,
linkcolor=magenta,
pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

% Customization for cos_prereg
\usepackage{longtable,booktabs,threeparttable,tabularx}
\linespread{1.5}
\newcounter{question}
\setcounter{question}{0}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist

\setlength{\droptitle}{-2em}
\title{Preregistration BIOL 520I - Productivity and Reproducibility}
\pretitle{\begin{changemargin}{-8pc}{0pc} \centering\large Preregistration\\ \Huge}
\posttitle{\end{changemargin}}
  \author{
          Harry Zhang\textsuperscript{1}          \\ \vspace{0.5cm}
              \textsuperscript{1} UBC Okanagan      }

  \def\affdep{{""}}%
  \def\affcity{{""}}%
  \preauthor{\begin{changemargin}{-8pc}{0pc} \centering\large}
  \postauthor{\end{changemargin}}
\date{25. September 2023}
\predate{\begin{changemargin}{-8pc}{0pc} \centering\large\emph}
\postdate{\end{changemargin}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\setlength{\headheight}{14.0pt}
\renewcommand{\headrulewidth}{0pt}
\lhead{}
\rhead{\large\textsc{\MakeLowercase{Preregistration BIOL 520I}}}



% Title settings
\usepackage{titlesec}
\titleformat{\section}[display]{\bfseries\Large}{\thesection}{}{}[]
\titlespacing{\section}{0pc}{*3}{*1.5}
\titleformat{\subsection}[leftmargin]{\titlerule\bfseries\filleft}{\thesubsection}{.5em}{}
\titlespacing{\subsection}{8pc}{5ex plus .1ex minus .2ex}{1.5pc}


% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi


\begin{document}
\maketitle
\vspace{2pc}


\ifPDFTeX
  \newcommand\Question[2]{%
   \leavevmode\par
   \stepcounter{question}
   \noindent
   \textbf{\thequestion. #1}. #2\par}
\else % if luatex or xetex
  \NewCommandCopy{\oldQuestion}{\Question}
  \renewcommand\Question[2]{%
   \leavevmode\par
   \stepcounter{question}
   \noindent
   \textbf{\thequestion. #1}. #2\par}
\fi



\newcommand\Answer[1]{%
    \noindent
    \textit{Registered response}: #1\par}

\hypertarget{data-collection}{%
\subsection{Data collection}\label{data-collection}}

\begin{quote}
This project uses existing data from the \emph{palmerpenguins} package.
\end{quote}

\hypertarget{hypothesis}{%
\subsection{Hypothesis}\label{hypothesis}}

\begin{quote}
This is an exploratory analysis without a priori hypothesis.
\end{quote}

\hypertarget{dependent-variable}{%
\subsection{Dependent variable}\label{dependent-variable}}

\begin{quote}
Although correlationship between variables is explored, no regression
method is used. Dependent variables are not defined.
\end{quote}

\hypertarget{conditions}{%
\subsection{Conditions}\label{conditions}}

\begin{quote}
NA
\end{quote}

\hypertarget{analyses}{%
\subsection{Analyses}\label{analyses}}

\begin{quote}
Group-wise statistics are calculated and presented in tabular formats to
show differences in penguin bill dimension.
\end{quote}

\hypertarget{outliers-and-exclusions}{%
\subsection{Outliers and exclusions}\label{outliers-and-exclusions}}

\begin{quote}
Rows with missing data are excluded from the analyses for simplicity.
\end{quote}

\hypertarget{sample-size}{%
\subsection{Sample size}\label{sample-size}}

\begin{quote}
344 observations are included in the raw data.
\end{quote}

\hypertarget{other}{%
\subsection{Other}\label{other}}

\begin{quote}
Observed data are plotted to aid visualization of bill dimension
differences.
\end{quote}

\hypertarget{study-type}{%
\subsection{Study type}\label{study-type}}

Finally. For record keeping purposes, please tell us the type of study
you are pre-registering.

\begin{itemize}
\tightlist
\item
  Class project or assignment
\end{itemize}

\hypertarget{references}{%
\section{References}\label{references}}

\emph{Horst AM, Hill AP, Gorman KB (2020). palmerpenguins: Palmer
Archipelago (Antarctica) penguin data. R package version 0.1.0.
\url{https://allisonhorst.github.io/palmerpenguins/}.
\url{doi:10.5281/zenodo.3960218}.}

\vspace{-2pc}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{-1in}
\setlength{\parskip}{8pt}

\noindent

\end{document}
